---
title: "Untitled"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
rm(list=ls())
getwd()
setwd("~/GitHub/LearnMachineLearn/healthcareai")

library(ggplot2)
library(healthcareai)
```


``````{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
df <- read.csv("SimData/SimData.csv")
```


```{r, results= 'hide', echo=FALSE, message=FALSE, warning=FALSE}
models <- machine_learn(df, patient_id, yrs_smoker, diabetes, outcome = diabetes_type)
```


```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
predictions <- predict(models)
plot(predictions)

ggplot(df, aes(predictions$diabetes_type, predictions$predicted_diabetes_type, 
               colour = predictions$diabetes_type)) + geom_point(alpha = 0.1)

plot(predictions$diabetes_type, predictions$predicted_diabetes_type, pch=19,
     col = rgb(red = 1, green = 0.2, blue = 0.5, alpha = 0.1),
     cex = 4)
```



```{r, results= 'hide', echo=FALSE, message=FALSE, warning=FALSE}
models <- machine_learn(df, patient_id, yrs_smoker, diabetes_type, outcome = diabetes)
```


```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
predictions <- predict(models)
plot(predictions)

ggplot(df, aes(predictions$diabetes_type, predictions$predicted_diabetes_type, 
               colour = predictions$diabetes_type)) + geom_point(alpha = 0.1)

plot(predictions$diabetes_type, predictions$predicted_diabetes_type, pch=19,
     col = rgb(red = 1, green = 0.2, blue = 0.5, alpha = 0.1),
     cex = 4)
```


```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#missingness(df) %>% 
#plot()
```
